Thesis Title

### 2022-10-20 chapters/introduction.tex
start conclusion

Clinical applications of \ac{SMg} derive their roots from the use of microarrays (see \secref{ssec:_intro_current_standards}), which it was successfully applied in in-depth microbiome analysis of different sites in the human body, it was the emergence of the second-generation sequencing technology and its high throughput of genomic data at a competitive price that made sequencing of all genomic content, \ac{DNA} and/or RNA, in a clinical sample a viable possibility for diagnostics (see \secref{ssec:_intro_2nd_gen_seq} The second-generation of \ac{DNA} sequencing) \citep{miller_basic_2009, palmer_rapid_2006, chiu_clinical_2019}. The first reported case that demonstrated the utility of \ac{SMg} was in 2014 with the clinical diagnosis of neuroleptospirosis in a 14-year-old immunodeficient and critically ill boy with meningoencephalitis by Wilson et al \cite{wilson_actionable_2014}, prompting appropriate targeted antibiotic treatment and eventual recovery of the patient. In this case, traditional methods, including an invasive brain biopsy, failed to provide answers, until the shotgun sequencing of cerebrospinal fluid identified 475 of 3,063,784 sequence reads (0.016\%) corresponding to leptospira, for which clinical assays were negative due to its very low abundance. Ever since many other reports of successful application of \ac{SMg} in clinical metagenomics have been reported. but all in edge cases where traditional diagnostic methods have failed or as proof-of-concept \citep{couto_critical_2018, vijayvargiya_application_2019, sanabria_shotgun-metagenomics_2020, hirakata_application_2021}.

>>>>

Clinical applications of \ac{SMg} derive their roots from the use of microarrays (see \secref{ssec:_intro_current_standards}), which it was successfully applied in in-depth microbiome analysis of different sites in the human body, it was the emergence of the second-generation sequencing technology and its high throughput of genomic data at a competitive price that made sequencing of all genomic content, \ac{DNA} and/or RNA, in a clinical sample a viable possibility for diagnostics (see \secref{ssec:_intro_2nd_gen_seq} The second-generation of \ac{DNA} sequencing) \citep{miller_basic_2009, palmer_rapid_2006, chiu_clinical_2019}. The first reported case that demonstrated the utility of \ac{SMg} was in 2014 with the clinical diagnosis of neuroleptospirosis in a 14-year-old immunodeficient and critically ill boy with meningoencephalitis by Wilson et al \cite{wilson_actionable_2014}, prompting appropriate targeted antibiotic treatment and eventual recovery of the patient. In this case, traditional methods, including an invasive brain biopsy, failed to provide answers, until the shotgun sequencing of cerebrospinal fluid identified 475 of 3,063,784 sequence reads (0.016\%) corresponding to leptospira, for which clinical assays were negative due to its very low abundance. Ever since many other reports of successful application of \ac{SMg} in clinical metagenomics have been reported. but all in edge cases where traditional diagnostic methods have failed or as proof-of-concept \citep{couto_critical_2018, vijayvargiya_application_2019, sanabria_shotgun-metagenomics_2020, hirakata_application_2021, he_case_2022}.
